A Fast Engine for Multi-string Pattern Matching

### 2017-02-04 response.tex

\documentclass{paper}

\title{Author's response to the review of No.IJPRAI-D-16-00429}

\begin{document}

\begin{center}
{\Large \textbf{Author's response to the review of No.IJPRAI-D-16-00429\\[20pt]}}
\end{center}

\textbf{Dear Editors and Reviewers:\\}

We would like to thank the reviewers and associate editors for their
valuable and constructive comments and suggestions. Based on these
comments and suggestions, we revised the paper, and the main revisions
are as follows.\\

\begin{center}
\textbf{Revisions Based on the Comments of Reviewer 1}\\
\end{center}

\textbf{1.} The construction of AMT used a breadth-first search
strategy, why does not use a depth-first strategy instead? Is there
some inherent reasons? Please give an explanation.\\[7pt]
\noindent \textbf{Response:} There is no essential distinction between
the breadth-first strategy and the depth-first strategy in
constructing the AMT. If the breadth-first strategy is adopted, the
AMT will be built level by level; on the other hand, if the
depth-first strategy is used, the AMT will be built branch by
branch. But regardless of the strategies used, the final built AMTs
are the same. We choose the breadth-first strategy to build the AMT
level by level, and we have added this explanation to Section 5.1.\\

\textbf{2.} Is the hash function used in the "Hash Table" node
structure the same as in other algorithms such as WM and
Pre-filter+AC?\\[7pt]
\noindent \textbf{Response:} No, they are not the same. The hash
functions used by the WM and Pre-filter+AC algorithms apply
essentially to short strings which consist no more than 3 characters,
whereas the hash function used in the \emph{hash node} must be able to
process longer strings with more than 3 characters. Therefore, we
choose the \emph{shift-add-xor} hash family for the hash node to
process long
strings.\\

\textbf{3.} The chosen of the parameters is very important for
building the tree nodes. Please give a more detailed instruction to
the chosen of the parameters in section 6.1.\\[7pt]
\noindent \textbf{Response:} For String Arrays containing no more than
\textbf{4} strings, the simple linear search is faster than binary
search due to the complexity of binary search. The load factor of the
Hash Table is set to \textbf{0.5}, which is a good balance between
time and space. The parameters about the hash function are chosen from
its original paper, which are claimed to be very efficient. We have
tested that once $ndp > 100$, the hash table structure becomes more
efficient than the String Array structure. All these detailed
explanations for parameter
selections have been added to section 6.1.\\

\textbf{4.} The captions and some table items in table 2, 3 and 4 are
not very clear, please revise them.\\[7pt]
\noindent \textbf{Response:} The captions of Table 2, 3 and 4 are
revised. The \emph{Sing Char} and \emph{Single String} items in these
tables are modified to \emph{Map 1} and \emph{Single String Array}, respectively.\\

\begin{center}
\textbf{Revisions Based on the Comments of Reviewer 2}\\
\end{center}

\textbf{1.} Is the hash function used in the \emph{Hash Table} node structure
the same as in the filter module?\\[7pt]
\noindent \textbf{Response:} No, they are not the same. The hash
function used in the \emph{Hash Table} node comes from the
\emph{shift-add-xor} hash family which is able to process long
strings, whereas the hash function used in the filter module is
usually a direct map which maps a short string to its decimal
representation.\\

\textbf{2.} Please explain how the two parameters $N$ and $k$ are chosen in the
filter module.\\[7pt]
\noindent \textbf{Response:} If $lsp \leq 5$, set $k = 2$; otherwise,
set $k=3$. $N$ is set to be $|\Sigma|^k$. We have added this comments
to Section 4.\\

\textbf{3.} The authors choose to use a breadth-first strategy to
build the AMT, is it possible to use a depth-first strategy instead?
\noindent \textbf{Response:} Absolutely yes. Regardless of which
strategies are used, the final constructed AMTs are the same.

\textbf{4.} The example (Fig.2) in the filter module does not clearly
show the interaction with the verification module. Please add some
detailed illustrations.
\noindent \textbf{Response:} Every time the filter module detects a
potential matched position in the text (i.e., the last bit of
$MB~\&~QB$ is 1), the verification module is invoked to check if there
exists patterns starting at that position, and in the mean while, the
matching window stops at that position, once the verification
finishes, the filter module moves the matching window to the next
position. We have added this detailed procedure to Section 4.\\

\begin{center}
\textbf{Revisions Based on the Comments of Reviewer 3}
\end{center}

There is no comments from reviewer 3.\\

\begin{center}
\textbf{Revisions Based on the Comments of Reviewer 4}
\end{center}

\textbf{1.} The novelty or fresh new ideas is not very clear, does not
have enough comparisons with other methods in the literature.\\[7pt]
\noindent \textbf{Response:} The major contributions of this paper
are: 1. A novel data structure called Adaptive Matching Tree (AMT) is
proposed to store the string pattern set efficiently. 2. A fast engine
based on AMT is proposed, which is able to process large-scale string
pattern sets. In addition, we have added another comparison with
a recent algorithm to the experiment part of our paper.\\

\textbf{2.} What is its relation to PR \& AI ? (Pattern Recognition \&
Artificial Intelligence) Should explain it more clearly.\\[7pt]
\noindent \textbf{Response:} The term \emph{pattern} has various
meanings in various fields. In this paper, the term \emph{pattern} is
specified to \emph{string pattern}, and accordingly \emph{pattern
  recognition} is specified to \emph{string pattern searching}, which
is one of the
oldest and fundamental problems in computer science.\\

\textbf{3.} Need to add more recent related publications in the
reference list including , for examples 2015, 2016 PR \& AI subfield.\\[7pt]
\noindent \textbf{Response:} We have already added several recent
published (in 2015 or 2016) references
about PR \& AI to our paper.\\

\textbf{4.} Compare your work with others in the literature,
advantages vs disadvantages, in depth and width.\\[7pt]
\noindent \textbf{Response:} We have added another comparison in our
experiment to a recent published multi-string pattern matching
algorithm called \textsf{Split} proposed by \emph{Kim, HyunJin AND
  Choi, Kang-Il AND Choi, Sang-Il. A Memory-Efficient Deterministic
  Finite Automaton-Based Bit-Split String Matching Scheme Using
  Pattern Uniqueness in Deep Packet
  Inspection. PLOS ONE. vol.10. pp.1-24. 2015.}\\

\textbf{5.} Should use real images with noisy and testing samples set
size should be large enough to show your results are indeed
convincing,
reliable, and meaningful.\\[7pt]
\noindent \textbf{Response:} Unfortunately, our method only focuses
on string patterns, so it does not apply to images.\\

\textbf{6.} This paper is not very well written. Its English
presentation is not good enough. Should consult English technical
writing expert to help.\\[7pt]
\noindent \textbf{Response:} We have carefully revised the paper again
to improve its presentation, so we hope it is more readable and easy
to understand now.

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2017-02-04 A_Fast_Engine_for_Multi_string_Pattern_Matching(revised).tex
revised

\documentclass{article}

\usepackage[numbers]{natbib}
\citestyle{IEEEtran}

\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{color}
\newcommand{\SWITCH}[1]{\STATE \textbf{switch} (#1)}
\newcommand{\ENDPWITCH}{\STATE \textbf{end switch}}
\newcommand{\CASE}[1]{\STATE \textbf{case} #1\textbf{:} \begin{ALC@g}}
\newcommand{\ENDCASE}{\end{ALC@g}}
\newcommand{\CASELINE}[1]{\STATE \textbf{case} #1\textbf{:} }
\newcommand{\DEFAULT}{\STATE \textbf{default:} \begin{ALC@g}}
\newcommand{\ENDDEFAULT}{\end{ALC@g}}
\newcommand{\DEFAULTLINE}[1]{\STATE \textbf{default:} }
\newtheorem{mydef}{Definition}
\newtheorem{mylm}{Proposition}

@@

% \title{An Efficient Adaptive Architecture for Muliti-pattern Matching}
% \author{Zhan Peng  Yuping Wang}
 %\maketitle

@@

\bibliographystyle{alpha}

\begin{center}
{\Large An Fast Engine for Large-scale String Pattern Matching}
\end{center}

\begin{abstract} 
  Multi-string matching is the core technique that is widely used in
  many applications. In general, it searches a text string for all
  occurrences of some string patterns. However, as the number of
  string patterns increases, most of the existing algorithms suffer
  from two issues: the long matching time, and the high memory
  consumption. To address these issues, in this paper, a fast matching
  engine is proposed for large-scale string matching problems. Our
  engine includes a filter module and a verification module. The filter
  module is based on several bitmaps, which is response for quickly
  filtering out the invalid positions in the text, while for each
  potential matched position, the verification module confirms true
  pattern occurrence. In particular, we design a compact data
  structure called Adaptive Matching Tree (AMT) as the verification
  module, in which each tree node saves some pattern fragments of the
  whole pattern set. The key point is that, the inner structure of
  each tree node is chosen adaptively according to the features of the
  corresponding pattern fragments, and this makes the whole AMT both
  time and space efficient for verifying. The experiments indicate
  that, our matching engine performs better than the prior algorithms,
  especially for large pattern sets.
\end{abstract}

{\textbf{Key words}: String Matching; Pattern Matching; Dictionary Matching}

@@

The MSM is a primitive but critical operation used in many
applications such as information retrieval, intrusion detection
system, information extraction, text editing, etc. In general, it
seeks all positions in a text string that match any of the string
patterns in a given pattern set. Efficient algorithms for MSM scan the
text only once, searching for all patterns
concurrently. Traditionally, these algorithms include two major
phases, i.e. the \textsf{preprocessing phase} and the \textsf{matching
  phase}. In the \textsf{preprocessing phase}, a suitable data
structure is constructed to store all the string patterns, and then
the \textsf{matching phase} scans and compares the given text with the
data structure for finding all occurrences every pattern in the
text. It is obvious that the time and space efficiency of the data
structure built in the preprocessing phase can have a significant
impact on the performance of the algorithm in the matching phase.

% Preferably, an algorithm scans the text once so that its performance
% should mainly depend on the size of the text rather than the features
% of pattern sets. However, the performance of lots of existing
% algorithms for MSM is affected seriously by the pattern sets. For
% instance, many algorithms, such as the classical \textsf{Wu-Manber}
% (\textsf{WM}) algorithm or the more recent \textsf{Pre-filter+AC}
% scheme, can not efficiently deal with the pattern sets containing very
% short patterns. When encountering such pattern sets, the performance
% of these algorithm degrades dramatically. This is due to the internal
% design of the data structure which is used for
% matching. {\color{red}{Therefore, it's quite valuable to design a data
% structure that can efficiently support pattern sets with various
% features. Using this kind of data structure can improve the robustness
% of MSM.}}

In the big data context nowadays the number of patterns to be matched
becomes huge in some applications, for instance, the database of a
modern anti-virus/intrusion-detection system can easily contain
millions, or even tens of millions number of virus
signatures/rules. However, the existing algorithms are not suitable
for such applications with very large pattern sets. Because on the one
hand, the throughout of these methods can not keep up with the demand
of the applications as the number of patterns increases, which is due
to the poor scalability of the data structures used by these methods,
and on the other hand, the data structure of several algorithms (such
as the \textsf{AC} algorithm) is not space efficient, which means they
can not process large pattern sets with limited memory. Therefore it
is very valuable to design space-efficient data structures with good
scalability to support applications requiring large-scale string
matching.

In this paper, we propose a multi-string matching engine for large
string pattern sets. Similarly to the traditional approaches, our
strategy consists of the preprocessing phase and the matching
phase. In the preprocessing phase, the matching engine is constructed
based on the pattern set. Then in the matching phase, the engine takes
the text string as input, and searches the occurrences of each
pattern in the text.

The proposed engine consists of a filter module and a verification
module. The function of the filter module is to find the potential matched
positions in the text. Once such a position is found, the verification
module confirms whether there are patterns starting at that
position. The filter we adopted is proposed by \cite{Lee2013}, which
is based on several bitmaps and a group of simple bitwised \emph{and}
and \emph{shift} operations. In the matching phase, the engine queries
the bitmaps to check the validity of the current position: if the
current position is a potential matched position, the verification
unit is invoked; otherwise, the engine skips over this position (as
well as the next few positions if possible). In particular, the
authors proved that the proposed filter is optimal in the sense that
it is able to utilizing all previous query results, which means the
filter can skip as many invalid positions as possible. For the
verification module, we design a compact tree-like data structure called
Adaptive Matching Tree (\textsf{AMT}) based on the pattern
set. Specifically, the whole pattern set is gradually partitioned into
several small parts first, and then the pattern fragments of each
small part is stored in a separate node of the AMT for subsequent
matching. The key point is that, the inner structure of each tree node
is selected adaptively according to the features of the pattern
fragments, and this adaptivity guarantees a high matching speed as
well as a low memory consumption for each tree node, as a result, the
whole AMT would be both time and space efficient for verifying in the
matching phase.

The rest of this paper is organized as follows: Section
\ref{sec:related works} reviews some related works in MSM. Section
\ref{sec:notations} lists the notations and terminology used in this
paper. Section \ref{sec:ADSM} describes our matching engine in
details. Section \ref{sec:experiments} presents the performance
evaluations. Section \ref{sec:conclusion} concludes the paper and
proposes some open problems.

@@

Because of the importance of PM, several efficient algorithms have
been proposed in the past decades. Well-known algorithms for PM
include Knuth-Morris-Pratt (\textsf{KMP}) \cite{Knuth1977},
Boyer-Moore (\textsf{BM}) \cite{Boyer1977}, Wu-Manber (\textsf{WM})
\cite{Wu1994}, and Aho-Corasick (\textsf{AC}) \cite{Aho1975}. The
\textsf{KMP} and \textsf{BM} algorithms are appropriate for SPM, but
not suitable for MPM. The \textsf{AC} algorithm is a generalization of
the \textsf{KMP} algorithm, by preprocessing the patterns and building
a deterministic finite automaton (DFA) that can match multiple
patterns simultaneously. It is the first algorithm for MPM that has a
linear time complexity. However, the \textsf{AC} algorithm is
alphabet-sensitive and requires a huge amount of memory to build the
DFA, which limits its application in large-scale pattern matching.

To reduce the memory requirement of \textsf{AC}, Tuck[2004] proposed a
algorithm called \textsf{Bitmapped AC}. This algorithm uses the bitmap
data structure to replace the conventional child pointers in each
state. In addition, it uses a path compression technique which can
merge successive single-child states into one state. It is reported
that, the compression optimization of \textsf{Bitmapped AC} results in
a 50 times reduction in memory consumption over the default
\textsf{AC} algorithm. However, since traversal from node to node
requires checking a bit in a bitmap and then performing a sum up to
256 prior bits in the bitmap, the average performance of this
algorithm is not high.  Another algorithm to reduce the space
requirement is the \textsf{Compressed AC} algorithm proposed by
Bremeler-Barr[2011]. In addition to use a similar path compression
method, this algorithm also develops a technique that can eliminate
the leaf states. The experiment shows that \textsf{Compressed AC} can
reduce at most $60\%$ memory requirement compared with the
traditionally \textsf{AC} algorithm. But the similar problem is, it
only works well for a few pattern sets.  Lee[2013] proposed an
algorithm called \textsf{Pre-filter+AC}. As the name shows, this
algorithm consists of a pre-filter and a verification engine. The
function of the pre-filter is to query data structures built from
patterns to find the starting positions of potential pattern
occurrences. Once a suspicious starting position is found, the
verification engine confirms true pattern occurrence. The pre-filter
uses a bit vector, called master bitmap, with simple bitwise-AND and
shift operations to accumulate query results. While the verification
engine, which is a modification of the AC automaton, checks all
candidate patterns simultaneously rather than sequentially. However,
as the author stated, the pre-filter is suitable for patterns of
moderate or large lengths. For short patterns, its throughput
degrades.

@@

To improve the \textsf{WM} algorithm, Zhou \cite{Zhou2007} proposed an
algorithm called \textsf{MDH}. Instead of using the first $m$
characters as the signature of each pattern, \textsf{MDH} adopts a
heuristic strategy to select the optimum $m$ consecutive characters as
the signature of each pattern. Similarly, Zhan \cite{Zhan2014}
proposed a different way to search for the optimal signatures of the
patterns, additionally, this algorithm designs an index structure to
reduce the time for searching the candidate patterns in the Hash
Table. These algorithms can improve the performance of \textsf{WM} for
common patterns but they do not solve the inefficiency caused by short
patterns. To address this problem, Zhang \cite{Zhang2009} proposed the
High Concurrence WM algorithm (\textsf{HCWM}), which separates the
patterns whose length is less than 4 from the pattern set. For these
short patterns, the algorithm establishes independent data structures
and uses different matching routines. This method can reduce the
effect of short patterns, since short patterns are matched
independently and concurrently. Another algorithm for this problem is
the \textsf{$L^{+1}$-MWM} proposed by Choi \cite{Choi2011}, which
minimizes the performance degradation caused by the short patterns by
appending characters to these patterns. It is reported that, the
\textsf{$L^{+1}$-MWM} improves the performance of WM by as mush as
$20\%$ in average, moreover, when $lsp < 5$ the \textsf{$L^{+1}$-MWM}
gains an $38.87\%$ enhancement.

For large scale pattern matching, which becomes more and more
important in big data context, Le \cite{Le2013} presented a
Memory-efficient Architecture for large-scale String Matching
(\textsf{MASM}) based on a pipelined binary search tree. It uses a
technique called ``leaf-attaching'' to compress the given pattern
set. The compressed pattern set are then transformed to a pipelined
binary tree tree which will be used in the matching phase. It is
reported that, the \textsf{MASM} achieves a memory efficiency (defined
as the ratio of the amount of the required storage in bytes and the
size of the pattern set in number of characters) of 0.56 for the
Rogets dictionary and 1.32 for the Snort rule set. Moraru
\cite{Moraru2012} also presented a memory-efficient and
cache-optimized algorithm for large pattern sets. This algorithm
builds upon the Rabin-Karp \cite{Karp1987} SPM algorithm and
incorporates a new \textsf{feed-forward} bloom filter which takes into
account the memory hierarchy of modern computers. This algorithm is
also well suited for implementation on GPUs which enables the matching
to be done in parallel.

@@

Nowadays, some variants of the classical MPM problem have been
proposed. Tomohiro \cite{I2015} introduced a variant of MPM, where the
pattern set is given in a compressed form that can be represented by a
straight line program (SLP). For a given SLP-compressed pattern set of
size $n$ and height $h$, which represents $m$ patterns of total length
$N$, they present an $O(n^2log^N)$-size variant of AC automaton that
recognizes all occurrences of the patterns in $O(h + m)$ running time
per character. Khancome \cite{Khancome2013} proposed an algorithm for
the dynamic MPM problem. This algorithm uses the \textsf{inverted
  lists} data structure to allow the pattern set to be updated
dynamically in a optimal time. Amir \cite{Amir2015} introduced an
algorithm for the gapped MPM problem, where each pattern in the
pattern set is a sequence of sub-patterns separated by bounded
sequences of do not cares. Neuburger \cite{Neuburger2012} presented
the first efficient algorithm that operates in small space for the
2-dimensional MPM problem.

@@

% the whole pattern set is transformed to a compact tree-like structure
% called Adaptive Matching Tree (AMT), where each tree node is built
% adaptively to save the information of a small part of the pattern
% set. While in the matching phase, the built AMT is compared against
% the text string to search patterns in that string. The framework of
% constructing the AMT from the pattern set is introduced in Section
% \ref{subsec:amt}, and using the AMT to search patterns in the text
% string is described in Section \ref{subsec:matching}, finally
% adaptively creating the tree nodes is presented in Section
% \ref{subsec:nodes}.

The filter we adopted in our engine is proposed by \cite{Lee2013},
which is an improvement of the filter in the WM algorithm. Given the
pattern set, as in the WM algorithm, only the length-$lsp$ prefix of
each pattern are considering in constructing the filter, where $lsp$
is the \emph{length of the shortest pattern} in the pattern
set. Similar to WM, the filtering is based on character blocks (a
character block is a merely short string consisting of only a few
characters) rather than single characters. Given a block size $k$, the
filter includes $lsp-k+1$ membership query bitmaps denoted as $B_1$,
$B_2$, \dots, and $B_{lsp-k+1}$, where each bitmap is a vector of $N$
bits. Let $B_j[i]$, $0 \leq i \leq N - 1$, $1 \leq j \leq lsp-k+1$, be
the $i$-th bit of the $j$-th query bitmap, and $B_j[i]$ is set to 1
iff there exists a pattern $p_m$ such that $hash(p_m[j,k]) = i$
($p_m[j,k]$ is a $k$-symbol block starting at position $j$ of $p_m$),
where $hash$ is a hash function that maps a $k$-symbol block to an
integer in the range of $[0, N-1]$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Trim Size: 9.75in x 6.5in
%% Text Area: 8in (include Runningheads) x 5in
%% ws-ijprai.cls   :   8-8-2014
%% Class file to use with ws-ijprai.tex written in Latex2E.
%% The content, structure, format and layout of this style file is the
%% property of World Scientific Publishing Co. Pte. Ltd.
%% Copyright 2014 by World Scientific Publishing Co.
%% All rights are reserved.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

\documentclass{ws-ijprai}
\usepackage{enumerate}

\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{color}
\usepackage{pgfplots}

\newcommand{\SWITCH}[1]{\STATE \textbf{switch} (#1)}
\newcommand{\ENDPWITCH}{\STATE \textbf{end switch}}
\newcommand{\CASE}[1]{\STATE \textbf{case} #1\textbf{:} \begin{ALC@g}}
\newcommand{\ENDCASE}{\end{ALC@g}}
\newcommand{\CASELINE}[1]{\STATE \textbf{case} #1\textbf{:} }
\newcommand{\DEFAULT}{\STATE \textbf{default:} \begin{ALC@g}}
\newcommand{\ENDDEFAULT}{\end{ALC@g}}
\newcommand{\DEFAULTLINE}[1]{\STATE \textbf{default:} }
\newtheorem{mydef}{Definition}
\newtheorem{mylm}{Proposition}

@@

@@

\markboth{Zhan Peng et al.}{A Fast Engine for Multi-string Pattern Matching}

%%%%%%%%%%%%%%%%%%%%% Publisher's area please ignore %%%%%%%%%%%%%%%
%
\catchline{}{}{}{}{}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{A Fast Engine for Multi-string Pattern Matching}

\author{Zhan Peng, Yuping Wang\footnote{Corresponding author}~, Wei Yue}

\address{$^1$School of Computer Science and Technology\\
  Xidian University\\
  Xi'an, Shaanxi, 710071, China\\
   $^*$ywang@xidian.edu.cn
}

\maketitle

%begin{history}
%received{(Day Month Year)}
%revised{(Day Month Year)}
%accepted{(Day Month Year)}
%comby{(xxxxxxxxxx)}
%end{history}

\begin{abstract}
  Multi-string matching is a core technique searching a text string
  for all occurrences of some string patterns. It is widely used in
  many applications. However, as the number of string patterns
  increases, most of the existing algorithms suffer from two issues:
  the long matching time, and the high memory consumption. To address
  these issues, in this paper, a fast matching engine is proposed for
  large-scale string matching problems. Our engine includes a filter
  module and a verification module. The filter module is based on
  several bitmaps which are response for quickly filtering out the
  invalid positions in the text, while for each potential matched
  position, the verification module confirms true pattern
  occurrence. In particular, we design a compact data structure called
  Adaptive Matching Tree (AMT) for the verification module, in which
  each tree node only saves some pattern fragments of the whole
  pattern set and the inner structure of each tree node is chosen
  adaptively according to the features of the corresponding pattern
  fragments. This makes the engine time and space efficient. The
  experiments indicate that, our matching engine performs better than
  the compared algorithms, especially for large pattern sets.
\end{abstract}

\keywords{String Matching; Pattern Matching; Dictionary Matching}

@@

The MSM is a primitive but critical operation used in many
applications such as pattern recognition \cite{Yan2016},
\cite{Xiao2016}, ontology alignments \cite{Xue2015} \cite{Xue2016},
text classification \cite{Tang2015} \cite{Zhang2016}, intrusion detection system
\cite{Kim2015}, etc. In general, it seeks all positions in a text
string that match any of the string patterns in a given pattern
set. An efficient algorithm for MSM only needs to scan the text once
and finds all patterns concurrently. Traditionally, the existing
algorithms include two major phases, i.e. the \textsf{preprocessing
phase} and the \textsf{matching phase}. In the \textsf{preprocessing
phase}, a suitable data structure is constructed to store all the
string patterns, and then the \textsf{matching phase} scans and
compares the given text with the data structure to find all
occurrences of every pattern in the text. It is obvious that the time
and space efficiency of the data structure built in the preprocessing
phase can have a significant impact on the performance of the
algorithm in the matching phase.

Nowadays, the number of patterns to be matched becomes huge in some
applications, for instance, the database of a modern
anti-virus/intrusion-detection system can easily contain millions
number of virus signatures/rules. However, the existing algorithms are
not suitable for such applications with very large pattern sets due to
two main reasons: 1) The poor scalability of the data structures used;
2) The space inefficiency of the data structure used, which means
these algorithms can not process large pattern sets with limited
memory. Moreover, the existing algorithms are sensitive to the length
of the patterns, particularly the length of the shortest pattern. Many
algorithms can not efficiently deal with pattern set containing very
short pattern due to the poor robustness of their data
structures. Therefore, it is very valuable to design space-efficient
data structures with good scalability and robustness to support
applications requiring large-scale string matching.

In this paper, we propose a multi-string matching engine with good
robustness for large string pattern sets. Similarly to the existing
efficient approaches, our approach consists of the preprocessing phase
and the matching phase. In the preprocessing phase, the matching
engine is constructed based on the pattern set. Then in the matching
phase, the engine takes the text string as input, and searches the
occurrences of each pattern in the text.

The proposed engine consists of a filter module and a verification
module. The function of the filter module is to find the potential
matched positions in the text. Once such a position is found, the
verification module confirms whether there are patterns starting at
that position. The filter adopted is proposed in \cite{Lee2013}, which
is based on several bitmaps and a group of simple bit-wised
"\emph{and}" and "\emph{shift}" operations. In the matching phase, the
engine queries the bitmaps to check the validity of the current
position: if the current position is a potential matched position, the
verification module is invoked; otherwise, the engine skips over this
position as well as the next few positions as many as possible. In
fact, the filter is proved to be optimal in the sense that it is able
to utilizing all previous query results, and thus can skip as many
invalid positions as possible. For the verification module, we design
a compact tree-like data structure called Adaptive Matching Tree
(\textsf{AMT}) based on the pattern set. Specifically, the whole
pattern set is gradually partitioned into several small parts first,
and then the pattern fragments of each small part is stored in a
separate node of the AMT for subsequent matching. The critical feature
of AMT is that, the inner structure of each tree node is changed
adaptively according to the features of the pattern fragments, and
this adaptivity guarantees a high matching speed as well as a low
memory consumption for each tree node, as a result, the whole AMT
would be both time and space efficient for verifying in the matching
phase.

The rest of this paper is organized as follows: Section
\ref{sec:related works} reviews some related works in MSM. Section
\ref{sec:notations} lists the notations and terminology used in this
paper. Section \ref{sec:filter} describes the filter module. Section
\ref{sec:verification} presents the verification module. Section
\ref{sec:experiments} presents the performance evaluations. Section
\ref{sec:conclusion} concludes the paper and proposes some open
problems.

@@

Because of the importance of PM, several efficient algorithms have
been proposed in the past decades. Well-known algorithms for PM
include Knuth-Morris-Pratt (\textsf{KMP}) \cite{Knuth1977},
Boyer-Moore (\textsf{BM}) \cite{Boyer1977}, Wu-Manber (\textsf{WM})
\cite{Wu1994}, and Aho-Corasick (\textsf{AC}) \cite{Aho1975}. The
\textsf{KMP} and \textsf{BM} algorithms are appropriate for SPM, but
not suitable for MPM. The \textsf{AC} algorithm is a generalization of
the \textsf{KMP} algorithm by preprocessing the patterns and building
a deterministic finite automaton (DFA) that can match multiple
patterns simultaneously. It is the first algorithm for MPM that has a
linear time complexity. However, the \textsf{AC} algorithm is
alphabet-sensitive and requires a huge amount of memory to build the
DFA, which limits its application in large-scale pattern matching.

To reduce the memory requirement of \textsf{AC}, Tuck \cite{Tuck2004}
proposed an algorithm called \textsf{Bitmapped AC}. This algorithm
uses the bitmap data structure to replace the conventional child
pointers in each state. In addition, it uses a path compression
technique which can merge successive single-child states into one
state. It is reported that, the compression optimization of
\textsf{Bitmapped AC} results in a 50 times reduction in memory
consumption over the default \textsf{AC} algorithm. However, since
traversal from node to node requires checking a bit in a bitmap and
then performing a sum up to 256 prior bits in the bitmap, the average
performance of this algorithm is not high.  Another algorithm to
reduce the space requirement is the \textsf{Compressed AC} algorithm
proposed by \cite{Bremler2011}. In addition to use a similar path
compression method, this algorithm also develops a technique that can
eliminate the leaf states. The experiment shows that
\textsf{Compressed AC} can reduce at most $60\%$ memory requirement
compared with the traditionally \textsf{AC} algorithm. But it only
works well for problems with a few pattern sets. Lee \cite{Lee2013}
proposed an algorithm called \textsf{Pre-filter+AC}. As the name
shows, this algorithm consists of a pre-filter and a verification
engine. The function of the pre-filter is to query data structures
built from patterns to find the starting positions of potential
pattern occurrences. Once a suspicious starting position is found, the
verification engine confirms true pattern occurrence. The pre-filter
uses a bit vector, called master bitmap, with simple bitwise-AND and
shift operations to accumulate query results. While the verification
engine, which is a modification of the AC automaton, checks all
candidate patterns simultaneously rather than sequentially. However,
as the author mentioned, the pre-filter is suitable for patterns of
moderate or large lengths. For short patterns, its throughput
degrades. Recently, Kim \cite{Kim2015} proposed a memory-efficient
algorithm \textsf{Split} for deep packet inspection system, which
consists of multiple finite-state machine.

@@

To improve the \textsf{WM} algorithm, Zhou \cite{Zhou2007} proposed an
algorithm called \textsf{MDH}. Instead of using the first $m$
characters as the signature of each pattern, \textsf{MDH} adopts a
heuristic strategy to select the optimum $m$ consecutive characters as
the signature of each pattern. Similarly, Zhan \cite{Zhan2014}
proposed a different way to search for the optimal signatures of the
patterns, additionally, this algorithm designs an index structure to
reduce the time for searching the candidate patterns in the Hash
Table. These algorithms can improve the performance of \textsf{WM} for
common patterns but they do not solve the inefficiency caused by short
patterns. To address this problem, Zhang \cite{Zhang2009} proposed the
High Concurrence WM algorithm (\textsf{HCWM}), which separates the
patterns whose length is less than 4 from the pattern set. For these
short patterns, the algorithm establishes independent data structures
and uses different matching routines. This method can reduce the
effect of short patterns, since short patterns are matched
independently and concurrently. Another algorithm for this problem is
the \textsf{$L^{+1}$-MWM} proposed by Choi \cite{Choi2011}, which
minimizes the performance degradation caused by the short patterns by
appending characters to these patterns. It is reported that, the
\textsf{$L^{+1}$-MWM} improves the performance of WM by as mush as
$20\%$ in average, moreover, when $lsp < 5$ the \textsf{$L^{+1}$-MWM}
gains a $38.87\%$ enhancement.

For large scale pattern matching, which becomes more and more
important in big data context, Le \cite{Le2013} presented a
Memory-efficient Architecture for large-scale String Matching
(\textsf{MASM}) based on a pipelined binary search tree. It uses a
technique called ``leaf-attaching'' to compress the given pattern
set. The compressed pattern set are then transformed to a pipelined
binary tree which will be used in the matching phase.  It is reported
that, the \textsf{MASM} achieves a memory efficiency (defined as the
ratio of the amount of the required storage in bytes and the size of
the pattern set in number of characters) of 0.56 for the Rogets
dictionary and 1.32 for the Snort rule set. Moraru \cite{Moraru2013}
also presented a memory-efficient and cache-optimized algorithm for
large pattern sets. This algorithm builds upon the Rabin-Karp
\cite{Karp1987} SPM algorithm and incorporates a new
\textsf{feed-forward} bloom filter which takes into account the memory
hierarchy of modern computers. This algorithm is also well suited for
implementation on GPUs which enables the matching to be done in
parallel.

@@

Nowadays, some variants of the classical MPM problem have been
proposed. Tomohiro \cite{I2015} introduced a variant of MPM, where the
pattern set is given in a compressed form that can be represented by a
straight line program (SLP). For a given SLP-compressed pattern set of
size $n$ and height $h$, which represents $m$ patterns of total length
$N$, they present an $O(n^2log^N)$-size variant of AC automaton that
recognizes all occurrences of the patterns in $O(h + m)$ running time
per character. Khancome \cite{Khancome2013} proposed an algorithm for
the dynamic MPM problem. This algorithm uses the \textsf{inverted
  lists} data structure to allow the pattern set to be updated
dynamically in an optimal time. Amir \cite{Amir2015} introduced an
algorithm for the gapped MPM problem, where each pattern in the
pattern set is a sequence of sub-patterns separated by bounded
sequences of do not cares. Neuburger \cite{Neuburger2012} presented
the first efficient algorithm that operates in small space for the
2-dimensional MPM problem.

@@

The filter we adopted in our engine is proposed by \cite{Lee2013},
which is an improvement of the filter in the WM algorithm. Given the
pattern set, as in the WM algorithm, only the length-$lsp$ prefix of
each pattern are considered in constructing the filter, where $lsp$ is
the \emph{length of the shortest pattern} in the pattern set. Similar
to WM, the filtering is based on character blocks (a character block
is merely a short string consisting of only a few characters) rather
than single character. Assuming that each block consists of $k$
characters, the filter will include $lsp-k+1$ membership query bitmaps
denoted as $B_1$, $B_2$, \dots, and $B_{lsp-k+1}$, where each bitmap
is a vector of $N$ bits. (If $lsp \leq 5$, set $k = 2$; otherwise, set
$k=3$. $N$ is set to be $|\Sigma|^k$). Let $B_j[i]$,
$0 \leq i \leq N - 1$, $1 \leq j \leq lsp-k+1$, be the $i$-th bit of
the $j$-th query bitmap, and $B_j[i]$ is set to 1 iff there exists a
pattern $p_m$ such that $hash(p_m[j,k]) = i$ ($p_m[j,k]$ is a
$k$-symbol block starting at position $j$ of $p_m$), where $hash$ is a
hash function that maps a $k$-symbol block to an integer in the range
of $[0, N-1]$.

\begin{figure}[htbp]
  \centering
  \includegraphics[height=2in, width=2in]{./eps/filter}
  \caption{The filter constructed from three digital patterns.}
  \label{fig:filter}
\end{figure}
